Should I Airbnb my Property?: Executive Summary

### 2017-03-19 abb_ExecSumm.Rmd
Adding websites to Exec Summary

---
title: "Should I Airbnb my Property?:  \n Executive Summary"
author: "Andy Krause and Gideon Aschwanden"
date: "March 13, 2017"
output: pdf_document
---

@@

>>>>

---
title: 'Should I Airbnb my Property?: Executive Summary'
author:
- Andy Krause
- '&'
- Gideon Aschwanden
- University of Melbourne
date: "March 13, 2017"
output:
  pdf_document: default
  html_document: default
---

@@

Finally, all code used to create this analysis can be found at:  [www.github.com/andykrause/airbnbMelbourne](https://www.github.com/andykrause/airbnbMelbourne).  An interactive website that allows for deeper exploration of the data and intermediate results is available at: [andykrause.shinyapps.io/ShouldIAirbnb](https://andykrause.shinyapps.io/ShouldIAirbnb).
